The error in Bayesian phylogenetic reconstruction when speciation is not instantaneous

### 2018-06-06 article.tex
Add 'rampal' command
Reword

For both data sets, we plot the nLTT statistics distribution per
parameter set using a violin plot, as such a plot 
maintains information about the distribution. To simplify the interpretation
of these plots, only nLTT statistics distribution are shown 
for $\lambda_g = \lambda_i$ and $\mu_g = \mu_i$. The general parameter set plot
does not make an additional separation between site model and clock model, but these
are shown in the appendix. The sampling parameter set plot does separate 
on the sampling method used.

>>>>

For both data sets, we display the nLTT statistics distribution per
biological parameter combination as a violin plot.
We only show combinations for which $\lambda_g = \lambda_i$ and $\mu_g = \mu_i$,
to simplify the interpretation of these results.

parameter set using a violin plot, as such a plot 
maintains information about the distribution. 
does not make an additional separation between site model and clock model. but these
are shown in the appendix. The sampling parameter set plot does separate 
on the sampling method used.
